Response Letter for manuscript TSG-01885-2017 ``Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints'' \\ \vspace{4mm} \large by Bahram~Alinia, Mohammad~H.~Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada

### 2019-08-25 TSC/Response-TSC.tex

\documentclass[11pt]{article}

\usepackage[paper=a4paper,dvips,top=4cm,left=2.5cm,right=2.5cm,
foot=2cm,bottom=4cm]{geometry}
%\usepackage{float}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amssymb,amsmath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{color,soul}
\usepackage{ragged2e} 
\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{subfigure}
%\usepackage{flushend}

% *** CITATION PACKAGES ***
%
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\graphicspath{{figRes/}{../}}

\usepackage[caption=false,font=footnotesize]{subfig}
%
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float

\newcommand{\sa}{\textsc{SmartAllocate}}
\newcommand{\rc}{\textsc{ReConsider}}
\newcommand{\bc}{\textsc{BetaCover}}
\newcommand{\ics}{\textsc{iCS}\xspace}
\newcommand{\fcs}{\textsc{fCS}\xspace}
\newcommand{\MCSP}{\textsf{SPAN}\xspace}
\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
\newcommand{\focs}{\textsc{foCS}\xspace}
\newcommand{\iocs}{\textsc{ioCS}\xspace}
\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
\newcommand{\opt}{\textsc{OPT}\xspace}
\newcommand{\alg}{\textsc{ALG}\xspace}
\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
\newcommand{\iolp}{\textsc{ioLP}\xspace}
\newcommand{\folp}{\textsc{foLP}\xspace}

\ifodd 1
\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
\newcommand{\com}[1]{\textbf{\color{red}(Bahram says: #1)}}%comment of the text
\newcommand{\comm}[1]{\textbf{\color{red}(Mohammad says: #1)}}%comment of the text
\else
\newcommand{\rev}[1]{#1}
\newcommand{\com}[1]{}
\fi

\usepackage[colorinlistoftodos, textwidth=4cm, shadow]{todonotes}
\newcommand{\bahram}[1]{\todo[inline,color=orange!40]{{\it Bahram:~}#1}}
\newcommand{\enrique}[1]{\todo[inline,color=blue!15]{#1}}
\begin{document}

\title{Response Letter for manuscript TSG-01885-2017 ``Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints'' \\
	\vspace{4mm} \large
	by  Bahram~Alinia, Mohammad~H.~Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada
}

\maketitle

\textbf{Dear Editor,}

We are very grateful for handling our paper and the time and effort that you and your team put into the process. We have thoroughly revised our manuscript based on your and the referees' constructive comments. This document provides a summary of changes made in the revised manuscript and detailed responses to the comments of the reviewers. The major changes in the revised manuscript are summarized below:

\begin{enumerate}
\item \textit{Better articulation of the paper's positioning, contribution, and significance}. 
\begin{itemize}
\item To highlight the positioning of our work among the extensive literature in EV charging scheduling, we added further explanations in Introduction to determine the exact scenario of interest among others. While several related work consider  EV scheduling in low-load regimes, our work tackle the resource-limited EV scheduling in high-load regimes. More details are given in response to Comment 3.1. 
\item We added a new Related Work Section in the revision (Section II) to highlight the positioning, contribution, and difference of our work as compared to the existing literature. The organization of the related work is based on the constructive Comment 1.0.3 of Reviewer 1. More details are given in response to Comments 1.0.1 and 1.0.3.
\item We re-organized and improved our the motivation statement and unique challenges of tackling ``global peak constraints'' in Introduction by considering Caltech ACN as a real example, \rev{clarifying the technical differences between scheduling problem with and without the global peak constraint}.  More details are given in response to Comment 2.2.
\end{itemize}
\item \textit{Better presentation and making the paper to be self-contained.} We have failed in our previous version of the paper to present our work in a self-contained manner. In the revision we compiled a 10-page manuscript by adding two new sections on Related Work (Section II) and offline algorithm design (Section IV-A), to the main manuscript. As mentioned in the previous item, related work helps to clarify the positioning, contribution, and significance of our work. In addition, with offline algorithm design in the main body, we do not refer to any algorithm in Appendix anymore, and it helps to follow the other online and offline algorithms easier. More details are given in responses to Comments 1.0.2 and 2.1.

\item \textit{More clarification on the valuation model}. Since we tackle EV charging scheduling in resource-limited scenarios with peak-constraints, we formulated a \rev{social welfare maximization problem} in which the goal is to achieve optimal revenue from the heterogeneous EVs with different valuations. We clarified the notion of valuation in system model in Section III-A in Page 3. More details are given in responses to Comments 1.2, 1.4, 2.3, and 3.1.

\item \textit{Re-implementation of all simulations and providing more explanations on simulation scenarios and setup.}  The EV battery properties including charging rates, etc., that we used in the first submission were not up-to-date according to the latest battery \rev{and chargers} technologies. In the revised version, we updated those properties and re-implemented all the simulations. We explained the simulation set-up in more details in Section VI. We combined two figures to save more space and provide more room and to be able to compare our proposed online and approximate algorithms to the optimal solution and existing algorithms in single plots. More details are given in responses to Comments 1.13, 1.14, 1.15, 1.16, 2.6, and 3.2.

\end{enumerate}

In what follows, we mention first the comments (as appeared in the decision letter, highlighted in {\color{blue} blue} in this letter) followed by a description on how we addressed those comments in the paper. Once again, thank you and your team for providing very constructive comments to help in improving this paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%\renewcommand{\thesection}{\arabic{count})}
%\newcounter{count}
%\stepcounter{count}
%\addtocounter{section}{1}
%\setcounter{section}{1}
{\Large\textbf{Editor's Comments:}}
\vspace{3mm}

{\color{blue}All three reviewers have expressed concern regarding the necessity of appendix, which makes the paper over the page limit set by this journal. The authors are advised to reduce the length of their paper. In addition, organization of the paper needs to be improved and contribution needs to be clarified.}

\vspace{5mm}
\noindent\textbf{Response:}
Based on the constructive comments, we revised the paper in 10 pages  by adding important contents such as literature review and an important technical contribution on offline algorithm design for fractional business model. 
By adding these contents and revising the paper carefully, the contribution of our paper is highlighted by demonstrating (1) the importance, uniqueness, and challenges of our specific problem motivated by observations from Caltech adaptive charging network; and (2) differences with the similar existing works in terms of system model, and proposed technical solutions.  More details are given in the aforementioned major comments and also the specific responses to the reviewers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Reviewer $\# 1$}
{\color{blue}}
%
%\vspace{4mm}
%{\color{blue}\noindent\\
%We sincerely appreciate you for taking the time to review
%our paper. Following the concerns and suggestions, the paper
%has carefully been revised to address the reviewer's comments
%properly.
%}

{\color{blue}The authors in this paper present two online algorithms to schedule EV charging for two different business models.}
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:}

We appreciate the reviewer's effort for his/her in-depth review. Below is our itemized response to this comment.

\vspace{3mm}
{\color{blue}
\textbf{1.0.1.} While the authors try to present extensive proof on the optimality of their algorithms, the problem of EV scheduling is an old problem and the problem authors discuss are no longer the most essential/important issues. 
 }
\vspace{3mm}

	$\vartriangleright$ \noindent\textbf{Response:}

We agree with the reviewer that the general EV scheduling problem has been studied extensively in the recent years, which demonstrates its importance in facilitating the deployment of EVs in energy systems. However, based on a real-world hierarchical architecture in the Adaptive Charging Network (ACN) in California Institute of Technology, in this work, we identified that the global peak constraint of the ACN results in a unique, yet challenging EV scheduling scenario that has not been addressed in the existing work.  Consequently, we formulated the corresponding EV scheduling problem and proposed solutions in two possible business models. Our experimental results also show that our scheduling mechanisms can achieve better performance as the existing scheduling practices in Caltech ACN, and at the same time the solutions can provide sound analytical performance guarantees. We further the positioning and significance of our paper in the highlighted parts of the Introduction.

	\vspace{3mm}
{\color{blue}	
\textbf{1.0.2.} The writing of the paper is quite confusing and hard to follow. It's more like a technical report that lacks good context. The authors simply cite certain algorithm from other paper without explaining it, making it very difficult for the reader to follow.}

\vspace{3mm}
	$\vartriangleright$ \noindent\textbf{Response:}

	This is because of the page limit in the first submission. 
	In the revised manuscript, we complied a 10-pages manuscript by reorganizing the paper and adding several important contents to the main body of the paper to make it self-contained. In particular, we added an optimal offline algorithm from our technical report to the revised manuscript with detailed explanations. Hence, in the revised version there is no more algorithm cited from other references or our technical report. The details of this algorithm is in Section IV-A, Pages 4-5 of the revised manuscript.

%\bibliography{ref-response}{}
%\vspace{-3mm}
%\bibliographystyle{ieeetr}

\end{document}

### 2019-08-25 TSC/R1/similarResponseLetters/ResponseLetter-tsg-submitMay11.tex

\documentclass[11pt]{article}

\usepackage[paper=a4paper,dvips,top=4cm,left=2.5cm,right=2.5cm,
foot=2cm,bottom=4cm]{geometry}
%\usepackage{float}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amssymb,amsmath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{color,soul}
\usepackage{ragged2e} 
\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{subfigure}
%\usepackage{flushend}

% *** CITATION PACKAGES ***
%
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\graphicspath{{figRes/}{../}}

\usepackage[caption=false,font=footnotesize]{subfig}
%
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\setlength{\intextsep}{-1ex} % remove extra space above and below in-line float

\newcommand{\sa}{\textsc{SmartAllocate}}
\newcommand{\rc}{\textsc{ReConsider}}
\newcommand{\bc}{\textsc{BetaCover}}
\newcommand{\ics}{\textsc{iCS}\xspace}
\newcommand{\fcs}{\textsc{fCS}\xspace}
\newcommand{\MCSP}{\textsf{SPAN}\xspace}
\newcommand{\dMCSP}{\textsf{dSPAN}\xspace}
\newcommand{\focs}{\textsc{foCS}\xspace}
\newcommand{\iocs}{\textsc{ioCS}\xspace}
\newcommand{\finalalg}{\textsc{ioCS+}\xspace}
\newcommand{\opt}{\textsc{OPT}\xspace}
\newcommand{\alg}{\textsc{ALG}\xspace}
\newcommand{\rtl}{\textsc{GreedyRTL}\xspace}
\newcommand{\iolp}{\textsc{ioLP}\xspace}
\newcommand{\folp}{\textsc{foLP}\xspace}

\ifodd 1
\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
\newcommand{\com}[1]{\textbf{\color{red}(Bahram says: #1)}}%comment of the text
\newcommand{\comm}[1]{\textbf{\color{red}(Mohammad says: #1)}}%comment of the text
\else
\newcommand{\rev}[1]{#1}
\newcommand{\com}[1]{}
\fi

\usepackage[colorinlistoftodos, textwidth=4cm, shadow]{todonotes}
\newcommand{\bahram}[1]{\todo[inline,color=orange!40]{{\it Bahram:~}#1}}
\newcommand{\enrique}[1]{\todo[inline,color=blue!15]{#1}}
\begin{document}

\title{Response Letter for manuscript TSG-01885-2017 ``Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints'' \\
	\vspace{4mm} \large
	by  Bahram~Alinia, Mohammad~H.~Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada
}

\maketitle

\textbf{Dear Editor,}

We are very grateful for handling our paper and the time and effort that you and your team put into the process. We have thoroughly revised our manuscript based on your and the referees' constructive comments. This document provides a summary of changes made in the revised manuscript and detailed responses to the comments of the reviewers. The major changes in the revised manuscript are summarized below:

\begin{enumerate}
\item \textit{Better articulation of the paper's positioning, contribution, and significance}. 
\begin{itemize}
\item To highlight the positioning of our work among the extensive literature in EV charging scheduling, we added further explanations in Introduction to determine the exact scenario of interest among others. While several related work consider  EV scheduling in low-load regimes, our work tackle the resource-limited EV scheduling in high-load regimes. More details are given in response to Comment 3.1. 
\item We added a new Related Work Section in the revision (Section II) to highlight the positioning, contribution, and difference of our work as compared to the existing literature. The organization of the related work is based on the constructive Comment 1.0.3 of Reviewer 1. More details are given in response to Comments 1.0.1 and 1.0.3.
\item We re-organized and improved our the motivation statement and unique challenges of tackling ``global peak constraints'' in Introduction by considering Caltech ACN as a real example, \rev{clarifying the technical differences between scheduling problem with and without the global peak constraint}.  More details are given in response to Comment 2.2.
\end{itemize}
\item \textit{Better presentation and making the paper to be self-contained.} We have failed in our previous version of the paper to present our work in a self-contained manner. In the revision we compiled a 10-page manuscript by adding two new sections on Related Work (Section II) and offline algorithm design (Section IV-A), to the main manuscript. As mentioned in the previous item, related work helps to clarify the positioning, contribution, and significance of our work. In addition, with offline algorithm design in the main body, we do not refer to any algorithm in Appendix anymore, and it helps to follow the other online and offline algorithms easier. More details are given in responses to Comments 1.0.2 and 2.1.

\item \textit{More clarification on the valuation model}. Since we tackle EV charging scheduling in resource-limited scenarios with peak-constraints, we formulated a \rev{social welfare maximization problem} in which the goal is to achieve optimal revenue from the heterogeneous EVs with different valuations. We clarified the notion of valuation in system model in Section III-A in Page 3. More details are given in responses to Comments 1.2, 1.4, 2.3, and 3.1.

\item \textit{Re-implementation of all simulations and providing more explanations on simulation scenarios and setup.}  The EV battery properties including charging rates, etc., that we used in the first submission were not up-to-date according to the latest battery \rev{and chargers} technologies. In the revised version, we updated those properties and re-implemented all the simulations. We explained the simulation set-up in more details in Section VI. We combined two figures to save more space and provide more room and to be able to compare our proposed online and approximate algorithms to the optimal solution and existing algorithms in single plots. More details are given in responses to Comments 1.13, 1.14, 1.15, 1.16, 2.6, and 3.2.

\end{enumerate}

In what follows, we mention first the comments (as appeared in the decision letter, highlighted in {\color{blue} blue} in this letter) followed by a description on how we addressed those comments in the paper. Once again, thank you and your team for providing very constructive comments to help in improving this paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

%\renewcommand{\thesection}{\arabic{count})}
%\newcounter{count}
%\stepcounter{count}
%\addtocounter{section}{1}
%\setcounter{section}{1}
{\Large\textbf{Editor's Comments:}}
\vspace{3mm}

{\color{blue}All three reviewers have expressed concern regarding the necessity of appendix, which makes the paper over the page limit set by this journal. The authors are advised to reduce the length of their paper. In addition, organization of the paper needs to be improved and contribution needs to be clarified.}

\vspace{5mm}
\noindent\textbf{Response:}
Based on the constructive comments, we revised the paper in 10 pages  by adding important contents such as literature review and an important technical contribution on offline algorithm design for fractional business model. 
By adding these contents and revising the paper carefully, the contribution of our paper is highlighted by demonstrating (1) the importance, uniqueness, and challenges of our specific problem motivated by observations from Caltech adaptive charging network; and (2) differences with the similar existing works in terms of system model, and proposed technical solutions.  More details are given in the aforementioned major comments and also the specific responses to the reviewers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Reviewer $\# 1$}
{\color{blue}}
%
%\vspace{4mm}
%{\color{blue}\noindent\\
%We sincerely appreciate you for taking the time to review
%our paper. Following the concerns and suggestions, the paper
%has carefully been revised to address the reviewer's comments
%properly.
%}

{\color{blue}The authors in this paper present two online algorithms to schedule EV charging for two different business models.}
\vspace{3mm}

$\vartriangleright$ \noindent\textbf{Response:}

We appreciate the reviewer's effort for his/her in-depth review. Below is our itemized response to this comment.

\vspace{3mm}
{\color{blue}
\textbf{1.0.1.} While the authors try to present extensive proof on the optimality of their algorithms, the problem of EV scheduling is an old problem and the problem authors discuss are no longer the most essential/important issues. 
 }
\vspace{3mm}

	$\vartriangleright$ \noindent\textbf{Response:}

We agree with the reviewer that the general EV scheduling problem has been studied extensively in the recent years, which demonstrates its importance in facilitating the deployment of EVs in energy systems. However, based on a real-world hierarchical architecture in the Adaptive Charging Network (ACN) in California Institute of Technology, in this work, we identified that the global peak constraint of the ACN results in a unique, yet challenging EV scheduling scenario that has not been addressed in the existing work.  Consequently, we formulated the corresponding EV scheduling problem and proposed solutions in two possible business models. Our experimental results also show that our scheduling mechanisms can achieve better performance as the existing scheduling practices in Caltech ACN, and at the same time the solutions can provide sound analytical performance guarantees. We further the positioning and significance of our paper in the highlighted parts of the Introduction.

	\vspace{3mm}
{\color{blue}	
\textbf{1.0.2.} The writing of the paper is quite confusing and hard to follow. It's more like a technical report that lacks good context. The authors simply cite certain algorithm from other paper without explaining it, making it very difficult for the reader to follow.}

\vspace{3mm}
	$\vartriangleright$ \noindent\textbf{Response:}

	This is because of the page limit in the first submission. 
	In the revised manuscript, we complied a 10-pages manuscript by reorganizing the paper and adding several important contents to the main body of the paper to make it self-contained. In particular, we added an optimal offline algorithm from our technical report to the revised manuscript with detailed explanations. Hence, in the revised version there is no more algorithm cited from other references or our technical report. The details of this algorithm is in Section IV-A, Pages 4-5 of the revised manuscript.

\vspace{3mm}
{\color{blue}
\textbf{1.0.3.} The authors state that most of the existing literature only discusses about optimal operation with single CS, which is not true. The field of EV Demand Side Management has long discussed the optimal operations with EV coordinations, renewable energy and battery storage, which is way beyond the simple scope of single CS scheduling. The reviewer recommends the writer to conduct more in-depth literature review. A good starting point may be "Mukherjee, Joy Chandra, and Arobinda Gupta. "A review of charge scheduling of electric vehicles in smart grid." IEEE Systems Journal 9.4 (2015): 1541-1553."
}

\vspace{3mm}
	$\vartriangleright$ \noindent\textbf{Response:}

We agree with the reviewer that there are extensive literature in the general area of EV demand side management and we have expanded our literature review in the revised version by citing the above survey and several other recent references  such as: 
	 \begin{itemize}
	 	\item P. M. de Quevedo, G. Mun ̃oz-Delgado, and J. Contreras, ``Impact of electric vehicles on the expansion planning of distribution systems considering renewable energy, storage and charging stations,'' IEEE Transactions on Smart Grid, 2017.

	 	\item 	 J. C. Mukherjee and A. Gupta, ``Distributed charge scheduling of plug-in electric vehicles using inter-aggregator collaboration'' IEEE Transactions on Smart Grid, vol. 8, no. 1, pp. 331--341, 2017.

	 	\item M. Shafie-Khah, P. Siano, D. Z. Fitiwi, N. Mahmoudi, and J. P. Catala ̃o, ''An innovative two-level model for electric vehicle parking lots in distribution systems with renewable energy,'' IEEE Transactions on Smart Grid, vol. 9, no. 2, pp. 1506--1520, 2018.
	 \end{itemize}
We fully understand that our statement in the beginning of Related Work section, was not accurate in the \textit{general area of EV demand side management}. We revised our related work to \textit{first} highlight that there are extensive work in this general research direction, and \textit{secondly}, we narrow down our review to those that tackle EV charging scheduling in single or multiple charging scheduling. With these modifications proposed by the reviewer the current version of the Related Work is more comprehensive and it highlights the uniqueness and importance of our work in more organized manner.
	 %And we fully understand that 
%	 However, we study the problem under a different system model which is based on Caltech adaptive charging network by considering local and global peak constraints while the local peak constraints can be over-provisioned. With the over-provisioned peaks, sum of the local peaks is more than the global peak. However, a proper centralized scheduling mechanism can intelligently allocate EVs in different charging stations such that a) resource utilization is maximized compared to non over-provisioned case, and b) the global peak constraint is not violated.
%Moreover, we considered two different business models (i.e., fractional and integral) and developed scheduling algorithms for both online and offline case.
%In addition, we provided extensive analysis regarding the competitive/approximation ratio of the algorithms.

\subsection{Comments}
%We sincerely appreciate you for taking the time to review our paper. Following the
%concerns and suggestions, the paper has carefully been revised to address the reviewer's
%comments properly.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.1:}\\
Page1 line 51: "Caltech ACN[4]". The reference is incorrect.
}}

\vspace{5mm}
\noindent\textbf{Response:}

Thanks for in-depth review of our paper. The cited reference includes an academic paper that describes the Caltech Adaptive Charing Network (ACN) and it is the only reference describing Caltech ACN.  
\\

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 1.2:}\\
Page 1 line 27: What does valuation mean? There is no clear definition for this value. It looks like a "bid" by each customer for their desired power. However, in current business model, the fee is mostly linearly correlated with the energy user uses, so this "valuation" should mostly be the energy demand of the user. However, it is true that the "valuation" could be more nuanced, given different user's profile, need and other background. If this is the case, it should be more clearly explained and the function for "valuation" should be more clearly defined.
}}

\vspace{5mm}
\noindent\textbf{Response:}

In this study, we consider the scenario in which the aggregate EV charging demands are beyond the local and global peak constraints of the adaptive charging network.  In this resource-limited scenario, it is rationale to solve a social welfare maximization problem with the goal of maximizing the aggregate \textit{utility} (in simplified case, \textit{valuation}, as we considered in our paper) of the users, i.e., EVs, in the system. In this way, the parameter $v_i$ denotes the willingness to pay (or valuation) of EV $i$ when it receives the entire demand $D_i$. We assume that $v_i$ is submitted by the user as the input to our optimization framework and it could be different for different users.

In the current business model, the aggregate charging demand is usually lower than the local and global peak constraints,  hence, the charging model pointed by the reviewer makes sense. This flat charging model, however, is not sustainable in the scenarios in which the peak constraint in the charging network hinders fulfilling the entire charging demand of the users and calls for new business models. As advocated in our study (and several other studies, for example \cite{robu2011online,gerding2011online,stein2012model}  in this letter and [8], [11], [12], [33] in the revised manuscript, in EV charging scheduling or in broader way in general utility maximization resource allocation problems), a natural way is to let EVs to announce their willingness to pay (valuations) and try to propose scheduling mechanisms that maximizes the aggregate valuation subject to the capacity constraints of the charging network.

%However, $v_i$ can carry different meanings depending on the application where the simplest interpretation is electricity price. In more complicated cases, $v_i$ can be priority or importance of the user, valuation of received power from the user/aggregator's point of view, etc. In such scenarios, $v_i$ is not a function of the demand. We solve the problem in a general case regardless of the meaning of input variable $v_i$.
%We made it clear in the paper that the valuation represents the profit of the charging station

 In the revised paper, we explained the clear definition of ``valuation'' of the EVs and the further justifications regarding this definition, in Section III-A2, in Page 3. In addition, in Introduction, we referred to the corresponding section for detailed definition of EV charging profiles (including valuations) right after the first appearance.

 %In simple and default case is the price imposed by charging station that the owner of EV $i$ should pay to receive its demand, $D_i$ (as it is in the paper). In this case, the charging station is allowed to use any pricing policy as it does not affect our algorithms. With this interpretation, our algorithms solve revenue maximization problem for utility provider. $v_i$ can also represent the valuation of demand from the user's point of view indicating that how much the user will be happy if it receives its submitted demand. With this interpretation, our algorithms try to maximize users' satisfaction or users' social welfare. Therefore, our proposed algorithms are general and work for any valuation setting that is proposed by either EVs or charging stations.
